Topic modeling on EU and the USA research projects

### 2017-06-28 thesis_report/draft_thesis.tex
Fix 5.2

In order to obtain an overall view of th etopics in EU, we calculated for each
one of the FPs the proportion of the documents-projects that are assigned to the
topics of the FP, normalized by the total number of the documents of the FP. The
topics that we are going to discuss in this section are the ones that either
show up in most of the FPs or they have a high percentage in one of them.

@@

With \emph{STEM} being the top priority in USA, since this topic shows up in all the years
and according to the plot in figure \ref{usatrend} \emph{STEM} is the topic with the highest proportion
of projects compared to the other topics (read section \ref{usaevolution}), 
most of the projects founded by
NSF are related to engineering, computer science, mathematics and
information systems, in general. The subjects \emph{STEM \& Education},
\emph{Software engineering}, \emph{Information systems} and \emph{Mathematics}, arise as
topics in all these years, from 1994-2017.

While NSF promotes the progress of science, it also enhances the efforts to
maintain the national health, prosperity, and welfare. Over the last 22 years,
many projects are related to the environment effects of climate change. Topics
like \emph{Environmental Science, Atmospheric \& Ocean sciences, Geology, Climate
change} and its impact in the United States emerge during all these years. The
last three years there is a focus on the \emph{Green energy production}, like
hydropower and wind power. Among with climate change, there is many research
related to \emph{Biology and Evolution}. A less popular subject that appears during the
years 1994-1997 and 2007-2013 is \emph{Molecular, Cellular \& Organismal biology and
Genetics}. These projects mostly refer to applied genetics, as well as cell
functionality. Topics include receptor biology, regulation of gene expression,
biomedical engineering, patterns of inheritance and molecular genetics.

Another popular subject that appears the last 22 years is \emph{Materials and
Chemistry}; the projects related to material research are mostly refer to the
materials' properties and applications in engineering. The last 3 years,
researchers from the USA focus on materials applications and design in
mechanical engineering, bioengineering and chemical \& transport systems. In
2002-2006 many projects are related to the subject of \emph{Transport} that is
sustainable in the senses of social, environmental and climate impacts (\emph{Green
transportation}).

NSF shows a great interest in \emph{International activities} across all NSF
supported disciplines. The goal of these projects is to support high
quality research and education, which could not occur without
international collaboration.
An interesting fact regarding international partnerships is that the
European Commission and the Government of the United States of America
concluded on 17 October 2016 an Implementing Arrangement that
simplifies the cooperation between Horizon 2020 projects and US
entities. European and American researchers will be able to work
together more closely on projects funded under Horizon 2020, the
European Union's \emph{Research and Innovation}
programme\footnote{\url{http://ec.europa.eu/research/iscp/index.cfm?pg=usa}}.

From 2002 up to day, \emph{Economic and Social Sciences} emerge as a topic in our
dataset. Researchers show a great interest in identifying policies which help
the communities and they also do lots of Qualitative and Quantitative research
to investigate the size or extent of particular issues or trends in society.

Finally, a topic that used to be popular in the past, in 1994-1997 and
2007-2013, is \emph{High energy Physics} in USA, which has lost its popularity
nowadays. The last 5 years, there is an interest around STEM and its
applications in \emph{manufacturing and engineering}.

\begin{figure}[H]
\begin{tabular}{rcl}
\subfloat[Software engineering]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
\subfloat[Climate change]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&
\subfloat[International research \& Education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic2_8000.png}}\\
\subfloat[Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic3_8000.png}}&
\subfloat[Economic \& Social science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic4_8000.png}} &
\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic5_8000.png}}\\
\subfloat[Molecular biology / Genetics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic6_8000.png}} &
\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic7_8000.png}}&
\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic8_8000.png}}\\
\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (1994-1997)}
\label{wordcloudUSA4}
\end{figure}

>>>>

In order to obtain an overall view of the topics in EU, we calculated for each
one of the FPs the proportion of the documents-projects that are assigned to the
topics of the FP, normalized by the total number of the documents of the FP. The
topics that we are going to discuss in this section are the ones that either
show up in most of the FPs or they have a high percentage in one of them.

@@

In order to obtain an overall view of the topics in USA, we calculated for each
one of the FPs the proportion of the documents-projects that are assigned to the
topics of the FP, normalized by the total number of the documents of the FP. The
topics that we are going to discuss in this section are the ones that either
show up in most of the FPs or they have a high percentage in one of them.

\emph{Biology} is a topic that appears all over the last 22 years that we
investigate, with a stable percentage of 10\% of the projects, on average. Some
of these topics are related to emph{Biology and Evolution}. Also, a 5\%
approximately of the projects are related to emph{Mathematics}, from 1994 to
2017.

Another popular subject that appears the last 22 years is \emph{Materials and
Chemistry}; the projects related to material research are mostly refer to the
materials' properties and applications in engineering. The last 3 years,
researchers from the USA focus on materials applications and design in
\emph{Mechanical engineering}, and \emph{Chemical \& transport systems}.

With \emph{STEM} being the top priority in USA, since this topic shows up in all
the years and according to the plot in figure \ref{usatrend} \emph{STEM} is the
topic with the highest proportion of projects compared to the other topics (read
section \ref{usaevolution}). Specifically, \emph{STEM education} has the 16,5\%
of the projects from 1994-2006, 21\% in 2007-2013 (1 out of 5 projects is
related to STEM) and the last 3 years it has lost its popularity by 10\%.

Moreover, \emph{Information systems} is a very popular subject from 1998 to 2013, 
covering the 13\% of the projects. The last 3 years, it became even more popular, 
since 1 out of 5 projects is related to \emph{Information systems}.

While NSF promotes the progress of science, it also enhances the efforts to
maintain the national health, prosperity, and welfare. From 1994 to 2013,
many projects are related to the environment effects of climate change. Topics
like \emph{Environmental Science, Atmospheric \& Ocean sciences, Geology, Climate
change} and its impact in the United States emerge during all these years in the 14\% 
of the projects, on average. The last three years \emph{Climate change} 
appears as a less popular subject (6\%).

NSF shows a great interest in \emph{International activities} across all NSF
supported disciplines (18\% of the projects in 1004-1998). The goal of these projects is 
to support high quality research and education, which could not occur without
international collaboration.
An interesting fact regarding international partnerships is that the
European Commission and the Government of the United States of America
concluded on 17 October 2016 an Implementing Arrangement that
simplifies the cooperation between Horizon 2020 projects and US
entities. European and American researchers will be able to work
together more closely on projects funded under Horizon 2020, the
European Union's \emph{Research and Innovation}
programme\footnote{\url{http://ec.europa.eu/research/iscp/index.cfm?pg=usa}}. The last
3 years, the projects related to \emph{International research} cover the 10\% of all the 
projects this period.

From 2002 up to day, \emph{Economic and Social Sciences} emerge as a topic in our
dataset (8\% of the projects, on average). Researchers show a great interest in identifying 
policies which help the communities and they also do lots of Qualitative and Quantitative 
research to investigate the size or extent of particular issues or trends in society.

Finally, a topic that used to be popular in the past, in 1994-1997 and
2007-2013, covering the 10\% of the projects funded by NSF, is \emph{High energy Physics} 
in USA, which has lost its popularity nowadays.

\begin{figure}[H]
\begin{tabular}{rcl}
\subfloat[Software engineering / STEM education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
\subfloat[Climate change]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&
\subfloat[International research \& Education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic2_8000.png}}\\
\subfloat[Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic3_8000.png}}&
\subfloat[Economic \& Social science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic4_8000.png}} &
\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic5_8000.png}}\\
\subfloat[Molecular biology / Genetics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic6_8000.png}} &
\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic7_8000.png}}&
\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic8_8000.png}}\\
\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (1994-1997)}
\label{wordcloudUSA4}
\end{figure}
